Supplementary Information

### 2015-08-28 manuscript/supplement.tex
Fixed figures

    \begin{figure}[h]
    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/LS_web.eps}}
    \caption{Estimates of the coefficients in equation XX do not vary significantly
    when jackknifing across food webs. We show the estimates (+/- 1SE) of each coefficient
    in the equation after the removal of each web in the dataset. All estimates are colour
    coded according the ecosystem type of the removed web.}
    \label{LS_web}
    \end{figure}

    \begin{figure}[h]
    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Gen_web.eps}}
    \caption{Estimates of the coefficients in equation XX do not vary significantly
    when jackknifing across food webs. We show the estimates (+/- 1SE) of each coefficient
    in the equation after the removal of each web in the dataset. All estimates are colour
    coded according the ecosystem type of the removed web.}
    \label{Gen_web}
    \end{figure}

    \begin{figure}[h]
    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Vul_web.eps}}
    \caption{Estimates of the coefficients in equation XX do not vary significantly
    when jackknifing across food webs. We show the estimates (+/- 1SE) of each coefficient
    in the equation after the removal of each web in the dataset. All estimates are colour
    coded according the ecosystem type of the removed web.}
    \label{Vul_web}
    \end{figure}

    \begin{figure}[h]
    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/LS_author.eps}}
    \caption{Estimates of the coefficients in equation XX do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the estimates (+/- 1SE) of each coefficient
    in the equation after the removal of all webs compiled by each author in the dataset.}
    \label{LS_web}
    \end{figure}

    \begin{figure}[h]
    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Gen_author.eps}}
    \caption{Estimates of the coefficients in equation XX do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the estimates (+/- 1SE) of each coefficient
    in the equation after the removal of all webs compiled by each author in the dataset.}
    \label{Gen_web}
    \end{figure}

    \begin{figure}[h]
    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Vul_author.eps}}
    \caption{Estimates of the coefficients in equation XX do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the estimates (+/- 1SE) of each coefficient
    in the equation after the removal of all webs compiled by each author in the dataset.}
    \label{Vul_web}
    \end{figure}

>>>>

    \begin{figure}[h]
    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/LS_web.eps}}
    \caption{Estimates of the coefficients in equation XX do not vary significantly
    when jackknifing across food webs. We show the estimates (with 95\% confidence intervals) of each coefficient
    in the equation after the removal of each web in the dataset. 
    The estimate for the full, non-jackknifed
    dataset is indicated by the red, dashed line. All estimates are colour
    coded according the ecosystem type of the removed web.}
    \label{LS_web}
    \end{figure}

    \begin{figure}[h]
    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Gen_web.eps}}
    \caption{Estimates of the coefficients in equation XX do not vary significantly
    when jackknifing across food webs. We show the estimates (with 95\% confidence intervals) of each coefficient
    in the equation after the removal of each web in the dataset. The estimate for the full, non-jackknifed
    dataset is indicated by the red, dashed line. All estimates are colour
    coded according the ecosystem type of the removed web.}
    \label{Gen_web}
    \end{figure}

    \begin{figure}[h]
    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Vul_web.eps}}
    \caption{Estimates of the coefficients in equation XX do not vary significantly
    when jackknifing across food webs. We show the estimates (with 95\% confidence intervals) of each coefficient
    in the equation after the removal of each web in the dataset.  The estimate for the full, non-jackknifed 
    dataset is indicated by the red, dashed line. All estimates are colour
    coded according the ecosystem type of the removed web.}
    \label{Vul_web}
    \end{figure}

    \begin{figure}[h]
    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/LS_author.eps}}
    \caption{Estimates of the coefficients in equation XX do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the estimates (with 95\% confidence intervals) of each coefficient
    in the equation after the removal of all webs compiled by each author in the dataset.
    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line.}
    \label{LS_web}
    \end{figure}

    \begin{figure}[h]
    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Gen_author.eps}}
    \caption{Estimates of the coefficients in equation XX do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the estimates (with 95\% confidence intervals) of each coefficient
    in the equation after the removal of all webs compiled by each author in the dataset.
    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line.}
    \label{Gen_web}
    \end{figure}

    \begin{figure}[h]
    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Vul_author.eps}}
    \caption{Estimates of the coefficients in equation XX do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the estimates (with 95\% confidence intervals) of each coefficient
    in the equation after the removal of all webs compiled by each author in the dataset.
    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line.}
    \label{Vul_web}
    \end{figure}
